On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-06 paper.tex
QED
Pyramid enlarged
For not to challenge readers' eyes.

As a result of independent significance, we show that increasing the delay from 1 to 2 enables an oritatami system to yield a conformation of quadratic length in $n$ as long as 5 types of beads are available.

@@

\begin{proposition}\label{prop:check_validity}
	For any rule set $R$, arity $\alpha$ and conformation $C = (P,w,H)$ it is possible to check whether $C$ is $R$-valid and whether $C\in \mathcal{C}_{\leq \alpha}$ in time $\mathcal{O}(|H|\cdot|w|\cdot|R|)$.
\end{proposition}
\begin{proof}
	To check whether $C$ is $R$-valid:
	\begin{enumerate}
		\item FOR each $(i,j)\in H$:
		\item \hspace{1cm} IF $(w[i],w[j])\notin R$ THEN answer NO and HALT
		\item answer YES and HALT
	\end{enumerate}	
	Checking the condition in 2. can be done in $\mathcal{O}(|w|\cdot|R|)$ time for any reasonable representation of $w$ and $R$, hence the whole process takes $\mathcal{O}(|H|\cdot |w|\cdot|R|)$ time.	
	To check the arity constraint $C\in \mathcal{C}_{\leq \alpha}$: 
	\begin{enumerate}
		\item FOR each $i\in \{1,\dots,|w|\}$:
		\item \hspace{1cm} IF $\mathrm{degree}(i)=|\{j | (i,j)\in H \}|>\alpha$ THEN answer NO and HALT
		\item answer YES and HALT
	\end{enumerate}	
	Checking the condition in 2. can be done in $\mathcal{O}(|H|)$ time for any reasonable representation of $H$, hence the whole process takes $\mathcal{O}(|w|\cdot|H|)$ time.
\end{proof}

\begin{theorem}\label{thm:OS_to_2dTM}
	There is an algorithm that simulates any deterministic oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$. 
\end{theorem}
\begin{proof}
	Take any step in the computation, up to which some $i \ge 0$ first beads of $w$ have been stabilized, with the last bead at a point $p$. 
	The number of all possible elongations of the current conformation by the next $\delta$-beads is $(6 \times 5^{\delta-1}) \times ((2^4)^{\delta-1} \times 2^5) \in 2^{O(\delta)}$. 
	By Proposition~\ref{prop:check_validity}, we can check for each of these elongations whether its arity is at most $\alpha$ or not and whether it is $R$-valid or not in time $\mathcal{O}((2^4)^{\delta-1}\cdot2^5\cdot \delta\cdot|R|)=2^{\mathcal{O}(\delta)}\cdot|R|$.  Therefore, the total running time is $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$.
\end{proof}

\begin{corollary}\label{cor:DTIME3}
	For fixed $\delta$, the class of problems solvable by deterministic oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(|w|^3)$.
\end{corollary}
\begin{proof}
	The claim follows from Theorem~\ref{thm:OS_to_2dTM} and the fact that $|R|$ is implicitly bounded by $|w|^2$.
\end{proof}

>>>>

As a result of independent significance, in Sect.~\ref{sect:lower}, we show that increasing the delay from 1 to 2 enables an oritatami system to yield a conformation of quadratic length in $n$ as long as 9 types of beads are available.

@@

\begin{proposition}\label{prop:check_validity}
	For any rule set $R$, arity $\alpha$ and conformation $C = (P,w,H)$ it is possible to check whether $C$ is $R$-valid and whether $C\in \mathcal{C}_{\leq \alpha}$ in time $\mathcal{O}(|H|\cdot|w|\cdot|R|)$.
\end{proposition}
\begin{proof}
	To check whether $C$ is $R$-valid:
	\begin{enumerate}
		\item FOR each $(i,j)\in H$:
		\item \hspace{1cm} IF $(w[i],w[j])\notin R$ THEN answer NO and HALT
		\item answer YES and HALT
	\end{enumerate}	
	Checking the condition in 2. can be done in $\mathcal{O}(|w|\cdot|R|)$ time for any reasonable representation of $w$ and $R$, hence the whole process takes $\mathcal{O}(|H|\cdot |w|\cdot|R|)$ time.	
	To check the arity constraint $C\in \mathcal{C}_{\leq \alpha}$: 
	\begin{enumerate}
		\item FOR each $i\in \{1,\dots,|w|\}$:
		\item \hspace{1cm} IF $\mathrm{degree}(i)=|\{j | (i,j)\in H \}|>\alpha$ THEN answer NO and HALT
		\item answer YES and HALT
	\end{enumerate}	
	Checking the condition in 2. can be done in $\mathcal{O}(|H|)$ time for any reasonable representation of $H$, hence the whole process takes $\mathcal{O}(|w|\cdot|H|)$ time.
	\qed
\end{proof}

\begin{theorem}\label{thm:OS_to_2dTM}
	There is an algorithm that simulates any deterministic oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$. 
\end{theorem}
\begin{proof}
	Take any step in the computation, up to which some $i \ge 0$ first beads of $w$ have been stabilized, with the last bead at a point $p$. 
	The number of all possible elongations of the current conformation by the next $\delta$-beads is $(6 \times 5^{\delta-1}) \times ((2^4)^{\delta-1} \times 2^5) \in 2^{O(\delta)}$. 
	By Proposition~\ref{prop:check_validity}, we can check for each of these elongations whether its arity is at most $\alpha$ or not and whether it is $R$-valid or not in time $\mathcal{O}((2^4)^{\delta-1}\cdot2^5\cdot \delta\cdot|R|)=2^{\mathcal{O}(\delta)}\cdot|R|$.  Therefore, the total running time is $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$.
	\qed
\end{proof}

\begin{corollary}\label{cor:DTIME3}
	For fixed $\delta$, the class of problems solvable by deterministic oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(|w|^3)$.
\end{corollary}
\begin{proof}
	The claim follows from Theorem~\ref{thm:OS_to_2dTM} and the fact that $|R|$ is implicitly bounded by $|w|^2$.
	\qed
\end{proof}
